Manuscript draft

### 2019-09-10 manuscript/Discussion_KAT.Rmd
Update Discussion_KAT.Rmd

In this analysis we used a comprehensive global database, containing an unprecedented amount of data and representing all global forest ecosystems and all significant forest carbon fluxes, to comprehensively explore the relationships between climate and productivity on a global scale. Many of our findings support and clarify previously published work; however we used a much larger and more complete database than has previously been available, allowing for higher quality control and standardisation of data. This enabled us to control for factors not previously controlled for - such as stand age, methodology, flux components, and disturbance regime - to gain a stronger understanding of latitudinal and climatic effects on productivity.

>>>>

We used a large global database (ForC), containing an unprecedented amount of data representing all major forest types (Fig. 1) and all significant forest autotrophic carbon fluxes (Table 2), to comprehensively explore how C cycling in mature forests varies with latitude and climate on a global scale. We test a suite of hypotheses, including many previously posed (Table 1), with more data and standardisation for factors that have not always been controlled for (*e.g.*, stand age, flux components measured) to gain a stronger understanding of climatic effects on productivity. We show that, across all nine productivity flux variables analyzed, C cycling decreases linearly with latitude (Figs. 2-3)--a finding that confirms multiple previous studies (**REFS**) but contradicts the idea that productivity of temperate forests rivals that of tropical forests (**REFS**). The flux variables increase in proportion to one another, with no differences in allocation detectable at this global scale and with component fluxes summing appropriately to larger fluxes (Fig. **2/3**), indicating no major, systematic omissions or overestimations of flux components. However, we did detect a tendency for greater variability among subsidiary C fluxes (Fig. **2/3**; **discussed below??**).
